Simulating a flock of birds

### 2017-11-01 tex/article.tex
Minor corrections
Comments on approx. of va

The behaviour of $v_a$ is found to be similar to that of the order parameter of some equilibrium systems close to their critical point. For large system sizes the data shows scaling which is an indication of a phase transition. Equations~\eqref{eq:va-eta} and~\eqref{eq:va-rho} may be used to describe such a system near the critical value, at which the phase transition occours.

@@

\begin{figure}[!htb]
\begin{center}
\includegraphics[width=\columnwidth]{va_over_angle}
\end{center}
\caption{Conevision}\label{fig:conevision}
\end{figure}

>>>>

The behaviour of $v_a$ is found to be similar to that of the order parameter of some equilibrium systems close to their critical point(like for example the magnetization in the 2D Ising model) if the density is high enough (Fig.2).
If the density is too low the system doesn't reach the disordered state where $v_a\approx 0$ or in other words it doesn't go through a phase transition.In our case the noise and density played the role of a temperature-like variable. Equations~\eqref{eq:va-eta} and~\eqref{eq:va-rho} may be used to describe such a system near the critical value, at which the phase transition occours.

@@

\begin{figure}[!htb]
\begin{center}
\includegraphics[width=\columnwidth]{va_over_angle}
\end{center}
\caption{The effect of the cone vision is only visible for adequately small densities}\label{fig:conevision}
\end{figure}
